---
title: "Data Science Capstone"
author: "Marco Xu"
date: "Saturday, April 25, 2015"
output: slidy_presentation
---

## Introduction

A predictive model which returns the most likely word to follow the current word. The vision is to put this into a text app such as SwiftKey, who not incidentally sponsored this capstone session. Thanks SwiftKey!

## Slide with R Code and Output
For example, if you input "I" as the first word
```{r}
library(shiny)
library(wordcloud)
setwd("H:\\open course\\introduction to Rprogramming Hopkins\\Data-Science-Capstone-Project\\shinny")
source("Predict.R")
predictedWords <-predictThis("I")
summary(predictedWords)
```

## Try to see What are the words predicted.

```{r}
predictedWords <-predictThis("I")
wordcloud(predictedWords[1:20], 
          c(20,15,12,10,8,6,4,3,3,3,3,3,3,3,3,3,3,3,3,3) ,
          random.order=F, max.words=200, colors=brewer.pal(8, "Dark2"))
```

## Let's make another pridiction with sevearal words.

```{r}
predictedWords <-predictThis("The guy in front of me just bought a pound of bacon, a bouquet, and a case of")
wordcloud(predictedWords[1:20], 
          c(20,15,12,10,8,6,4,3,3,3,3,3,3,3,3,3,3,3,3,3) ,
          random.order=F, max.words=200, colors=brewer.pal(8, "Dark2"))
```

Though beer is not the first-rank prediction, it appears to be the third choice.